### 2020-05-26 writeup/proofs_sec3.tex
add label
revise sec A

\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_main}

@@

We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.

\begin{lemma}\label{lem_minv}[\todo{ref?}]
	Let $X\in\real^{n\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$. Let $A$ be a $p\times p$ matrix that is independent of $X$ and satisfies $\|A\|=\OO(1)$.
	In the setting when $n = c p$ we have that
	\[  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{c - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \]
for any constant $\e>0$.
\end{lemma}

>>>>

\section{Supplementary Materials for Section \ref{sec_insight}}\label{app_proof_sec3}

@@

We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$. The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity. When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}. For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}. Here we shall state a result that is a consequence of Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound.

\begin{lemma}\label{lem_minv} 
	Let $X = \Sigma^{1/2} Z\in\real^{n\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma\in\real^{p\times p}$. Suppose the entries of $Z$ have finite moments up to any order. Let $A$ be a $p\times p$ matrix that is independent of $X$ and satisfies $\|A\|=\OO(1)$.
	In the setting when $n = \rho p$ for some constant $\rho>1$, we have that with high probability,
	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(A\Sigma^{-1}) +\bigo{ p^{-1/2+\epsilon}} \ee
for any constant $\e>0$.
\end{lemma}

In this section, we will always consider random variables with finite moments up to any order. On the other hand, if the entries of $Z$ have finite $a$-th moment for some constant $a>4$, then \eqref{XXA} still holds except that the error bound becomes  $\OO( p^{-\frac12+\frac2a +\epsilon})$; see our Corollary \ref{main_cor} below.
